My title

### 2023-03-15 outputs/paper/paper.qmd
Quarto paper edit
edits to the quarto paper

@@

# Table showing the first 10 rows of our cleaned dataset
cleaned_2016gss_data |> 
  select(age, sex, race, 
         degree, childs, marital,
         happy, wwwhr) |> 
  slice(1:8) |> 
  kable(caption='A subset of key features',
        col.names = c("Age", "Sex", "Race", "Highest Degree", 
                      "Number of Children", "Marital Status", "Happiness Level", 
                      "Weekly Internet Hours"),
        digits = 1,
        booktabs = FALSE,
        linesep = "") |>
  kable_styling(full_width = T)
```

>>>>

Saku :)

@@

# Table showing the first 10 rows of our cleaned dataset
cleaned_2016gss_data |> 
  select(wwwhr, age, sex, race, 
         degree, childs, marital,
         happy) |> 
  slice(1:8) |> 
  kable(caption='A subset of key features',
        col.names = c("Weekly Internet Hours", "Age", "Sex", "Race", "Highest Degree", 
                      "Number of Children", "Marital Status", "Happiness Level"),
        digits = 1,
        booktabs = FALSE,
        linesep = "") |>
  kable_styling(full_width = T)
```
